A note on observation processes in epidemic models

### 2019-07-31 ms/ms.tex
tweaks

We compared two scenarios in which newly infected cases are reported 
instantaneously (1) when individuals become infected or
(2) when they recover. Although neither of these
assumptions is realistic, many epidemic models still rely on these
assumptions (see Introduction). 
More realistic models may distinguish reported and unreported
(i.e., identified and unidentified) cases by adding
new state variables \citep{browne2015modeling,webb2015model} 
or by modeling an explicit delay kernel in reporting time 
\citep{harris1990reporting, ferguson2001foot, ster2009epidemiological, 
birrell2011bayesian, funk2018real}.

@@

>>>>

We compared two scenarios in which newly infected cases are reported 
instantaneously (1) when individuals become infected or
(2) when they recover. Although neither of these
assumptions is realistic, many epidemic models still rely on these
assumptions (see Introduction). 
More realistic models may distinguish reported and unreported
(i.e., identified and unidentified) cases by adding
new state variables \citep{browne2015modeling,webb2015model} 
or by modeling an explicit delay distribution in reporting time 
\citep{harris1990reporting, ferguson2001foot, goldstein2009reconstructing,
ster2009epidemiological, birrell2011bayesian, funk2018real}.

@@

Here, we assumed that the underlying transmission process is deterministic; this 
assumes that all error can be explained by observation errors alone. 
We chose to study a deterministic model SIR for computational efficiency; 
we do not recommend using deterministic models for real outbreak analyses.
Ignoring process errors (i.e., stochasticity in the transmission process) can lead to
overly confident results \citep{king2015avoidable}. Using stochastic models may
even give better coverage probabilities when wrong observation models are used. 
Nonetheless, misspecifying the observation model can still affect conclusions from 
stochastic models and introduce bias.
